Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-05-22 inc/model_results/rf_cav/rf_cav.tex
tweaks to model_results rf_cav section

In comparison to using magnetic lenses to compensate for transverse pulse broadening by using magnetic lenses, RF cavities are being employed in UED systems~\cite{oudheusden_electron_2007}, and are expected to be employed in UEM systems as well, to compensate for longitudinal broadening in the ultrashort pulses.
\ref{fig:rf_cav_num} illustrates the operation of a $ \Omega / 2 \pi = $ 3GHz $\text{TM}_{010}$ RF cavity of axial length $ d = \pi v_{\smallzero} / \Omega $ as an electron pulse compressor tuned to produce the shortest pulse at a distance $ z^{\prime} = $ 10cm behind the cavity for $N=1$ and $N=10^5$ pulse charges.
The mathematical model of the RF cavity (see Section \ref{rf_cav_model}) employs $L_{RF} = d \approx $ 14mm, $ z^{\prime}_{RF} = 0 $, and a region of influence super-Gaussian of order 2 ($n=2$ in \ref{eq:reg_of_influence}) to reflect the sharper ends of the RF cavity.
In both cases, the idealized initial conditions are used, starting the pulse at $ z^{\prime} = -10$ cm, an excess photoemission energy $\Delta E = 0.5$ eV, velocity related to a $V_{DC} = $ 20kV acceleration potential, HW1/eM $ w = $ 0.1mm and duration $\tau = $ 100fs ($v_{\smallzero} \tau \approx 8.4 \mu$m).
This electron pulse is therefore initially in the preferred highly oblate regime ($ \sigma_{\smallT}(0) \gg \sigma_{z} (0) $), for which space-charge effects predominantly act in the longitudinal direction, broadening the pulse in time (see \ref{fig:compare_shape}).

@@

\ref{fig:rf_cav_num}\subref{fig:rf_cav_N1} depicts the optimized RF cavity performance with $N=1$ electrons in the pulse.
The internal pulse space-charge effects are negligible under these conditions, so that the RF cavity only compensates for the `dispersive' electron pulse broadening to $\sim$1.67ps at the RF cavity entrance that is due to the initial longitudinal momentum spread caused by the $\Delta E = $ 0.5eV excess photoemission energy.
For an RF field amplitude $E_{0} = $ 450 kV/m and phase $\phi = 0$, the dispersion-generated momentum chirp $\gamma_{z}$ is exactly reversed upon propagation through the RF cavity to produce a compressed pulse at $ z^{\prime} = $ 10cm behind the RF cavity.
In this case, the pulse is returned to its original temporal duration --- an exact 1-to-1 `temporal imaging' of the photo-generated electron pulse at $z' = -10$cm by the RF cavity to $ z' = $ 10cm.
On the other hand, the dynamics of the spatial size of the electron pulse are clearly affected by the negative compound transverse lens of the RF cavity (the magnetic contribution of the TM$_{010}$-mode plus the axial entrance and exit aperture electric fields, see Section \ref{rf_cav_model}), increasing at the temporal focus to a factor of $\sim 10\times$ its initial value.

>>>>

In comparison to using magnetic lenses to compensate for transverse pulse broadening by using magnetic lenses, RF cavities are being employed in UED systems~\cite{oudheusden_electron_2007}, and are expected to be employed in UEM systems as well, to compensate for longitudinal broadening in the ultrashort pulses.
\ref{fig:rf_cav_num} illustrates the operation of a $ \Omega / 2 \pi = $ 3GHz $\text{TM}_{010}$ RF cavity of axial length $ d = \pi v_{\smallzero} / \Omega $ as an electron pulse compressor tuned to produce the shortest pulse at a distance $ z^{\prime} = $ 10cm behind the cavity for $N=1$ and $N=10^5$ pulse charges.
The mathematical model of the RF cavity (see Section \ref{rf_cav_model}) employs $L_{RF} = d \approx $ 14mm, $ z^{\prime}_{RF} = 0 $, and a region of influence super-Gaussian of order 2 ($n=2$ in \ref{eq:reg_of_influence}) to reflect the sharper ends of the RF cavity.
In both cases, the idealized initial conditions are used, starting the pulse at $ z^{\prime} = -10$ cm, an excess photoemission energy $\Delta E = 0.5$ eV, velocity related to a $V_{DC} = $ 20kV acceleration potential, HW1/eM width $ w = $ 0.1mm and duration $\tau = $ 100fs ($v_{\smallzero} \tau \approx 8.4 \mu$m).
This electron pulse is therefore initially in the preferred highly oblate regime ($ \sigma_{\smallT}(0) \gg \sigma_{z} (0) $), for which space-charge effects predominantly act in the longitudinal direction, broadening the pulse in time (see \ref{fig:compare_shape}).

@@

\ref{fig:rf_cav_num}\subref{fig:rf_cav_N1} depicts the optimized RF cavity performance with $N=1$ electrons in the pulse.
The internal pulse space-charge effects are negligible under these conditions, so that the RF cavity only compensates for the `dispersive' electron pulse broadening to $\sim$1.67ps at the RF cavity entrance that is due to the initial longitudinal momentum spread caused by the $\Delta E = $ 0.5eV excess photoemission energy.
For an RF field amplitude $E_{0} = $ 450 kV/m and phase $\phi = 0$, the dispersion-generated momentum chirp $\gamma_{z}$ is exactly reversed upon propagation through the RF cavity to produce a compressed pulse at $ z^{\prime} = $ 10cm behind the RF cavity.
In this case, the pulse is returned to its original temporal duration --- an exact 1-to-1 `temporal imaging' of the photo-generated electron pulse at $z' = -10$cm by the RF cavity to $ z' = $ 10cm.
On the other hand, the dynamics of the spatial size of the electron pulse are clearly affected by the negative compound transverse lens of the RF cavity (the magnetic contribution of the TM$_{010}$-mode plus the axial entrance and exit aperture electric fields, see Section \ref{rf_cav_model}), increasing the pulse's width at the temporal focus to a factor of $\sim 10\times$ its initial value.

### 2013-05-22 inc/model_results/rf_cav/rf_cav_plot.tex
tweaks to model_results rf_cav section

\begin{figure}
  \centerline {
    \subfloat[][]{
      \label{fig:rf_cav_N1}
      \begin{tikzpicture}
        \input{rf_cav_N1}
      \end{tikzpicture}
    }
    \subfloat[][]{
      \label{fig:rf_cav_N1e5}
      \begin{tikzpicture}
        \input{rf_cav_N1e5}
      \end{tikzpicture}
    }
  }
  \caption[Short]{
    Long
  }
  \label{fig:rf_cav_num}
\end{figure}

>>>>

\begin{figure}
  \centerline {
    \subfloat[][]{
      \label{fig:rf_cav_N1}
      \begin{tikzpicture}
        \input{rf_cav_N1}
      \end{tikzpicture}
    }
    \subfloat[][]{
      \label{fig:rf_cav_N1e5}
      \begin{tikzpicture}
        \input{rf_cav_N1e5}
      \end{tikzpicture}
    }
  }
  \caption[Dynamics of the pulse length and width under the influence of an RF cavity]{
    Dynamics of the pulse length (green) and width (red) under the influence of an RF cavity placed at $z^{\prime} = 0$.
    The employed idealized pulses start at $z^{\prime} = -100\text{cm}$ with velocity $v_{\smallzero} \approx 84 \times 10^{6} \text{m/s}$ ($20\text{kV}$) and initial HW1/eM width of 100 $\mu$m and length $\sim 8.4 \mu\text{m}$ ($v_{\smallzero} \cdot 100\text{fs}$).
    \subref{fig:rf_cav_N1} has $N=1$ electron and demonstrates one-to-one imaging of the initial pulse length at the focus at $ z^{\prime} = 100 \text{cm}$.
    \subref{fig:rf_cav_N1e5} has $ N = 1 \times 10^5 $ electrons, whose added broadening allows for the factor of two reduction in pulse length at the focus ($\sim 48\text{fs}$).
  }
  \label{fig:rf_cav_num}
\end{figure}
